---
title: "Clairvoyant Project, Fall 2025"
author:
  - "Team Joey"
format:
  pdf:
    colorlinks: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
# Core libraries
library(readr)
library(dplyr)

# Plot helpers
source("R/plot_functions.R")

# Where to save images
OUT_DIR <- "output"
dir.create(OUT_DIR, recursive = TRUE, showWarnings = FALSE)
```

## Data

This report expects a cleaned dataset (CSV) produced by the pipeline.
By default, it loads `data/final_data.csv`.

```{r}
df <- read_csv("data/final_data.csv", show_col_types = FALSE)
```

## Industry Health Score

```{r}
p_industry_bar <- plot_top_industries_bar(df,
                        industry_col = "industry",
                        score_col = "industry_health_score")
save_plot(p_industry_bar, "industry_health_bar.png", out_dir = OUT_DIR)
p_industry_bar
```

## Industry Risk vs Return (size = job postings)

```{r}
df_labels <- summarize_industry_risk_return(
  df,
  industry_col = "industry",
  vol_col = "industry_vol_12m",
  ret_col = "industry_excess_return_12m",
  job_postings_col = "job_postings"
)

p_risk_return <- plot_industry_risk_return(df_labels)
save_plot(p_risk_return, "industry_risk_return.png", out_dir = OUT_DIR)
p_risk_return

```

## Distributions of key metrics

p_dist <- plot_distributions(```{r}
p_dist <- plot_distributions(
  df,
  cols = c(
    "views",
    "follower_count",
    "industry_health_score",
    "industry_return_12m",
    "industry_vol_12m",
    "company_health_score",
    "company_return_12m",
    "company_excess_return_12m",
    "company_vol_12m"
  )
)
save_plot(p_dist, "metric_distributions.png", out_dir = OUT_DIR)
p_dist
```)
```

## Correlation matrix (hiring signals vs company metrics)

```{r}
# Example: Communication Services correlation view
df_comms <- df %>%
  filter(industry == "communication services") %>%
  group_by(finance_name) %>%
  summarize(
    views = mean(views, na.rm = TRUE),
    follower_count = mean(follower_count, na.rm = TRUE),
    company_health_score = mean(company_health_score, na.rm = TRUE),
    company_return_12m = mean(company_return_12m, na.rm = TRUE),
    .groups = "drop"
  )

p_corr <- plot_correlation_matrix(
  df_comms,
  title = "Communication Services (company-level averages)",
  cols = c("views", "follower_count", "company_health_score", "company_return_12m")
)
save_plot(p_corr, "comms_correlation_matrix.png", out_dir = OUT_DIR)
p_corr
```
